Gammapy: A Python package for gamma-ray astronomy

### 2023-03-23 src/ms-review.tex
Add complete data reference for joint crab

With the public availability of the \gadf format specifications and the
\gammapy package, some experiments started to make limited subsets of
their \gammaray data publicly available for testing and validating
\gammapy. For example, the \hess collaboration released a limited test
dataset (about 50 hours of observations taken between 2004 and 2008)
based on the \gadf DL3 format \citep{HESS_DR1}. This data release served
as a basis for validation of open analysis tools, including \gammapy 
\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have been
%% CN: what about VERITAS and FACT?
 released by the \magic collaboration~\citep{magic_performance}, using which a
joint analysis across different gamma-ray instruments was first demonstrated in ~\cite{joint_crab}.
The \hawc collaboration also released
a limited test dataset of the Crab Nebula, which was used to validate
the \gammapy package in \cite{Olivera2022}.
%% CN: I would remark this also demonstrated Gammapy could be applied to WCD
%% depite having been designed for IACTs initially
The increased availability of public data that followed the definition of
a common data format, and the development of \gammapy as a community-driven open software,
led the way toward a more open science in the very-high-energy \gammaray astronomy domain.
The adoption of \gammapy as science tools strengthens the commitment of the future \cta Observatory to the FAIR principles
(Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
that define the key requirements for open science.

>>>>

With the public availability of the \gadf format specifications and the
\gammapy package, some experiments started to make limited subsets of
their \gammaray data publicly available for testing and validating
\gammapy. For example, the \hess collaboration released a limited test
dataset (about 50 hours of observations taken between 2004 and 2008)
based on the \gadf DL3 format \citep{HESS_DR1}. This data release served
as a basis for validation of open analysis tools, including \gammapy 
\cite[see e.g.][]{Mohrmann2019}. Two observations of the Crab nebula have
been released by the \magic collaboration~\citep{magic_performance}.
Using these public data from \fermi, \hess, \magic and additional observations
provided by FACT and \veritas, the authors of \cite{joint_crab} presented
a combined analysis of \gammaray data from different instruments for the first time.
Later the \hawc collaboration also released a limited test dataset of the Crab Nebula,
which was used to validate the \gammapy package in \cite{Olivera2022}.
%% CN: I would remark this also demonstrated Gammapy could be applied to WCD
%% depite having been designed for IACTs initially
The increased availability of public data that followed the definition of
a common data format, and the development of \gammapy as a community-driven open software,
led the way toward a more open science in the very-high-energy \gammaray astronomy domain.
The adoption of \gammapy as science tools strengthens the commitment of the future \cta Observatory to the FAIR principles
(Findable, Accessible, Interoperable and Reusable) principles \citep{FAIR16, FAIR22} 
that define the key requirements for open science.
